Thermodynamic fragments in magic state theories

### 2021-02-08 magic_paper.tex
minor additions
restructured coordinate analysis to be more legible, added red note on important fine print, but checked the rest numerically and have corrected minor errors

One of the most fundamental and commonly used magic monotones is the \emph{mana} of a state \nick{CITE}, defined as
\begin{equation}
    \mana{\rho} \coloneqq \log{(2\sn{\rho}+1)},
\end{equation}
where the \emph{sum-negativity} ($\rm{sn}$) \nick{CITE} is the sum of the negative components in $\W{\rho}$,
\begin{equation}
    \sn{\rho} \coloneqq \sum\limits_{\bmx: \W[\bmx]{\rho} < 0} \abs{\W[\bmx]{\rho}}.
\end{equation}
Mana is an additive\footnote{It satisfies the condition $\mana{\rho_1 \otimes \rho_2} = \mana{\rho_1} + \mana{\rho_2}$ which is practical is distillation settings.} magic monotone, so it provides a necessary condition for magic state interconvertibility.

@@

Given an even value $\alpha$ for the sum, the term $\wn^{n-\alpha} \wp^{\alpha} e^{-\beta (n-\alpha)E_0}$ is fixed, so the expression is maximised by setting the coefficient of the highest energy $E_{\rm{max}}$ equal to $\alpha$.
Hence, we have
\begin{align}
	\widetilde{W}_{\rm{max}} &= \max\limits_{\substack{\alpha = 0,2, \\ \dots,n-2,n}}{\Big\{ (-\wn)^{n-\alpha} \wp^{\alpha} e^{\beta (n-\alpha)E_0} e^{\beta \alpha E_{\rm{max}}} \Big\}} \\
	&= \max\limits_{\substack{\alpha = 0,2, \\ \dots,n-2,n}}{\Big\{ \wn^n e^{n\beta E_0} \left( \frac{u}{v} e^{\beta (E_{\rm{max}} - E_0)} \right)^{\alpha} \Big\}}
\end{align}
The last expression is clearly maximised for $\alpha = 0$ ($\alpha = n$) when the expression $\frac{u}{v} e^{\beta (E_{\rm{max}} - E_0)}$ is less than or equal to $1$ (greater than $1$).
We want to rewrite the expression as a noise level $\epsilon$ constraint with respect to temperature $\beta^{-1}$, where the noise threshold is
\begin{equation}
	\epsilon_{\rm{th}} \coloneqq 3 - \dfrac{18}{8-e^{(E_{\rm{max}} - E_0)\beta}}.
	%\beta \leq \frac{1}{E_{\rm{max}} - E_0}\ln{\left( 8-\frac{18}{3-\epsilon} \right)}
\end{equation}
The noise threshold $\epsilon_{\rm{th}}$ is an increasing function of temperature $\beta^{-1}$.
We have
\begin{equation}
\widetilde{W}_{\rm{max}} =
	\begin{cases}
		\wn^n e^{n\beta E_0}, &\epsilon \leq \epsilon_{\rm{th}}, 	\\
		\wp^n e^{n\beta E_{\rm{max}}}, &\epsilon > \epsilon_{\rm{th}}.
	\end{cases}
\end{equation}

For low noise levels $\epsilon \leq \epsilon_{\rm{th}}$, we get $\widetilde{W}_{\rm{max}} = \wn^n e^{n\beta E_0}$ occuring in the region labelled by $(i,j,k) = (0,0,0)$.
This scenario includes the unital fragment, defined at the limit $\beta \rightarrow 0$, because for $\beta = 0$, we have $\epsilon_{\rm{th}} = 3/7$, so $\epsilon \leq \epsilon_{\rm{th}}$ always holds.

In the low noise level scenario, the multiplicity is $m_{000} = 1$ and the first elbow coordinates can be read off the $X^0Y^0Z^0$ term in generating functions $G_n(\noisys), G_n(\gamma)$,
\begin{equation}
	(x_0, L_0) = ((3\Z)^{-n}, \wn^n)
\end{equation}
and the necessary distillation constraint defined at the location $x_\star = x_0$ of the initial state's first elbow is
\begin{equation}\label{eq:first_elbow_constraint}
	\lc{\noisys(\epsilon)\too{n}}{\gamma_\beta}(x_\star) \geq \lc{\noisys(\epsilon')\too{\tt}}{\gamma_\beta}(x_\star).
\end{equation}

The first elbow of the target state is located at $x'_0 = (3Z)^{-\tt} > x_\star$, so in order to find the target state Lorenz curve coordinate $L'_\star$ at location $x_\star$, we can interpolate between the origin and the target state's first elbow, 
\begin{equation}\label{eq:constraint_deriv_temp}
	L'_\star = \frac{x_\star}{x'_0}L'_0 = (3\Z_\beta)^{\tt-n} \left( \frac{1}{3} - \frac{4}{9} \epsilon' \right)^{\tt}.
\end{equation}
The process in~\cref{eq:msd_thermal} is therefore possible only if $L_\star \geq L'_\star$ or equivalently,
\begin{align}
	\frac{n}{n'} \geq \frac{\ln{\Big[ \big( 1-\frac{4}{3}\epsilon' \big)\Z_\beta \Big]}}{\ln{\Big[ \big( 1-\frac{4}{3}\epsilon \big)\Z_\beta \Big]}} = \frac{\ln{\big( 1-\frac{4}{3}\epsilon' \big)} - \beta F_\beta}{\ln{\big( 1-\frac{4}{3}\epsilon \big)} - \beta F_\beta},
\end{align}
with $\tt \leq n$ and $\epsilon' \leq \epsilon \leq \epsilon_{\rm{th}}$. 
The free energy of thermal state $\gamma_\beta$ is denoted by
\begin{equation}
	F_\beta \coloneqq \tr[\gamma_\beta H] - \beta^{-1} \tr[\gamma_\beta \log{\gamma_\beta}].
\end{equation}

Moreover, we can obtain an upper bound on thermal fragment distillation rate $R=n'/n$ for pure target Strange states ($\epsilon' = 0$) given by
\begin{equation}
	R \leq R(\beta) \coloneqq 1 - \frac{\ln{\big( 1-\frac{4}{3}\epsilon \big)}}{\beta F_\beta},
\end{equation}
which holds for all finite $n$ with $\tt \leq n$ and $\epsilon' \leq \epsilon \leq \epsilon_{\rm{th}}$. 
We compare $R(\beta)$ for different values of $\beta$ with the mana bound $R_{\rm{mana}}$ in~\cref{fig:distill_bounds_temp}.
\begin{figure}[h]
    \centering
    \includegraphics[scale=0.5]{figs/distill_bounds_temp.pdf}
    \caption{\textbf{Distillation rate with low noise in thermal fragments.} Distillation rates obtained by majorization $R(\beta)$ for low noise levels $\epsilon \leq \epsilon_{\rm{th}}$ are plotted for different temperatures $\beta^{-1}$ such that $0 \leq \beta \leq \beta_{\rm{th}}$.
    The mana distillation rate $R_{\rm{mana}}$ is given for comparison.
    As $\beta$ increases, the range of noise levels for which $R(\beta)$ is valid decreases and the distillation bound becomes stricter.
    }
    \label{fig:distill_bounds_temp}
\end{figure}

Our approach also allows for analysis at the limit of low temperature, $\beta \rightarrow \infty$.
In fact, for any
\begin{equation}
	\beta \geq \beta_{\rm{th}} \coloneqq \frac{1}{E_{\rm{max}} - E_0} \ln2,
\end{equation}
we always have $\epsilon_{\rm{th}} \leq 0$, so $\epsilon \geq \epsilon_{\rm{th}}$.
Note that if $E_{\rm{max}} = E_0$, the bound is infinite, simply meaning that $\epsilon = \epsilon_{\rm{th}}$ at the limit $\beta = \infty$.
In the low temperature scenario, we get $\widetilde{W}_{\rm{max}} = \wn^p e^{n\beta E_{\rm{max}}}$ occuring in a region labelled by 
\begin{equation}
	(i,j,k) = 
	\begin{cases}
	(n,0,0), &E_{\rm{max}} = E_0, \\
	(0,n,0), &E_{\rm{max}} = E_1, \\
	(0,0,n), &E_{\rm{max}} = E_2.
	\end{cases}
\end{equation}
The bound expression does not depend on which energy is the highest so, without loss of generality, assume that $E_{\rm{max}} = E_0$.
Then, the multiplicity is $m_{n00} = 2^n$ and the first elbow coordinates can be read off the $X^nY^0Z^0$ term in generating functions $G_n(\noisys), G_n(\gamma)$,
\begin{equation}
	(x_0, L_0) = \left( \left(\frac{2}{3}\frac{e^{-\beta E_0}}{\Z_\beta}\right)^n, (2u)^n \right)
\end{equation}
and the distillation constraint is defined at the location $x_\star = x_0$ of the initial state's first elbow as in~\cref{eq:first_elbow_constraint}.

The first elbow of the target state is located at $x'_0 = (2e^{-\beta E_0} / (2\Z_\beta))^{\tt} > x_\star$, so in order to find the target state Lorenz curve coordinate $L'_\star$ at location $x_\star$, we can interpolate between the origin and the target state's first elbow, 
\begin{equation}\label{eq:constraint_deriv_lowtemp}
	L'_\star = \frac{x_\star}{x'_0}L'_0 = 2^n \left(\frac{e^{-\beta E_0}}{3\Z_\beta}\right)^{n-\tt} \left( \frac{1}{6} - \frac{1}{18}\epsilon' \right)^{\tt}.
\end{equation}
Therefore, in the low temperature scenario $\beta \geq \beta_{\rm{th}}$, the distillation process in~\cref{eq:msd_thermal} is possible only if $L_\star \geq L'_\star$ or equivalently,
\begin{align}
	\frac{n}{n'} &\geq \frac{\ln{\Big[ \big( \frac{1}{2}-\frac{1}{6}\epsilon' \big)\Z_\beta e^{\beta E_{\rm{max}}} \Big]}}{\ln{\Big[ \big( \frac{1}{2}-\frac{1}{6}\epsilon \big)\Z_\beta e^{\beta E_{\rm{max}}} \Big]}} \nonumber\\
	&= \frac{\ln{\big( \frac{1}{2}-\frac{1}{6}\epsilon' \big)} + \beta (E_{\rm{max}} - F_\beta)}{\ln{\big( \frac{1}{2}-\frac{1}{6}\epsilon \big)} + \beta (E_{\rm{max}} - F_\beta)},
\end{align}
with $\tt \leq n$ and $\epsilon' \leq \epsilon$.

We can obtain an upper bound on thermal fragment distillation rate $R=n'/n$ for pure target Strange states ($\epsilon' = 0$) in this regime as well. 
It is given by
\begin{equation}
	R \leq R(\beta) \coloneqq 1 - \frac{\ln{\big(\frac{3}{3-\epsilon} \big)}}{-\ln{2} + \beta (E_{\rm{max}} - F_\beta)},
\end{equation}
which holds for all finite $n$ with $\tt \leq n$ and $\epsilon' \leq \epsilon$. 
We compare $R(\beta)$ for different values of $\beta$ with the mana bound $R_{\rm{mana}}$ in~\cref{fig:distill_bounds_lowtemp}.
\begin{figure}[h]
    \centering
    \includegraphics[scale=0.5]{figs/distill_bounds_lowtemp.pdf}
    \caption{\textbf{Distillation rate for low temperatures in thermal fragments.} Distillation rates obtained by majorization $R(\beta)$ in the temperature regime $\beta \geq \beta_{\rm{th}}$ are plotted for different temperatures $\beta^{-1}$.
    The mana distillation rate $R_{\rm{mana}}$ is given for comparison.
    \nick{Terrible bound for low temperatures. I'll check for possible calculation errors.}
    }
    \label{fig:distill_bounds_lowtemp}
\end{figure}

>>>>

One of the most fundamental and commonly used magic monotones is the \emph{mana} of a state \nick{CITE}, defined as
\begin{equation}
    \mana{\rho} \coloneqq \ln{(2\sn{\rho}+1)},
\end{equation}
where the \emph{sum-negativity} ($\rm{sn}$) \nick{CITE} is the sum of the negative components in $\W{\rho}$,
\begin{equation}
    \sn{\rho} \coloneqq \sum\limits_{\bmx: \W[\bmx]{\rho} < 0} \abs{\W[\bmx]{\rho}}.
\end{equation}
Mana is an additive\footnote{It satisfies the condition $\mana{\rho_1 \otimes \rho_2} = \mana{\rho_1} + \mana{\rho_2}$ which is practical is distillation settings.} magic monotone, so it provides a necessary condition for magic state interconvertibility.

@@

Given an even value $\alpha$ for the sum, the term $\wn^{n-\alpha} \wp^{\alpha} e^{-\beta (n-\alpha)E_0}$ is fixed, so the expression is maximised by setting the coefficient of the highest energy $E_{\rm{max}}$ equal to $\alpha$.
Hence, we have
\begin{align}
	\widetilde{W}_{\rm{max}} &= \max\limits_{\substack{\alpha = 0,2, \\ \dots,n-2,n}}{\Big\{ (-\wn)^{n-\alpha} \wp^{\alpha} e^{\beta (n-\alpha)E_0} e^{\beta \alpha E_{\rm{max}}} \Big\}} \\
	&= \max\limits_{\substack{\alpha = 0,2, \\ \dots,n-2,n}}{\Big\{ \wn^n e^{n\beta E_0} \left( \frac{u}{v} e^{\beta (E_{\rm{max}} - E_0)} \right)^{\alpha} \Big\}}
\end{align}
The last expression is maximised for $\alpha = 0$ ($\alpha = n$) when the expression $\frac{u}{v} e^{\beta (E_{\rm{max}} - E_0)}$ is less than or equal to $1$ (greater than $1$).
We want to rewrite the expression as a noise level $\epsilon$ constraint with respect to temperature $\beta^{-1}$, where the noise threshold is
\begin{equation}
	\epsilon_{\rm{th}} \coloneqq 3 - \dfrac{18}{8-e^{(E_{\rm{max}} - E_0)\beta}}.
	%\beta \leq \frac{1}{E_{\rm{max}} - E_0}\ln{\left( 8-\frac{18}{3-\epsilon} \right)}
\end{equation}
The noise threshold $\epsilon_{\rm{th}}$ is a decreasing function of $\beta$.
It achieves its maximum value $3/7$ for $(E_{\rm{max}} - E_0)\beta = 0$, and its minimum value $0$ for
\begin{equation}
	\beta_{\rm{th}} \coloneqq \frac{1}{E_{\rm{max}} - E_0} \ln2.
\end{equation}
We have
\begin{equation}
\widetilde{W}_{\rm{max}} =
	\begin{cases}
		\wn^n e^{n\beta E_0}, &\epsilon \leq \epsilon_{\rm{th}},\ \hspace{30pt}\rm{(C1)}	\\
		\wp^n e^{n\beta E_{\rm{max}}}, &\epsilon > \epsilon_{\rm{th}}.\ \hspace{32pt}\rm{(C2)} 
	\end{cases}
\end{equation}
Case 1 $\rm{(C1)}$ corresponds to the region labelled by $(i,j,k) = (0,0,0)$.
Case 2 $\rm{(C2)}$ corresponds to the region labelled by 
\begin{equation}
	(i,j,k) = 
	\begin{cases}
	(0,n,0), &\text{if } E_{\rm{max}} = E_1, \\
	(0,0,n), &\text{if } E_{\rm{max}} = E_2.
	\end{cases}
\end{equation}
Note that if $E_{\rm{max}} = E_0$, we get $\epsilon_{\rm{th}} = 3/7$ and $\rm{(C1)}$ holds for all $\epsilon$ and $\beta$.
Assuming $E_{\rm{max}} > E_0$, we get the cases:
\begin{itemize}
	\item $\beta = 0$. Then, $\epsilon_{\rm{th}} = 3/7$ and $\rm{(C1)}$ holds for all noise levels $\epsilon$.
	This is the unital fragment.
	\item $0 < \beta < \beta_{\rm{th}}$. Then, $0 < \epsilon_{\rm{th}} < 3/7$ and $\rm{(C1)}$ holds for $\epsilon \leq \epsilon_{\rm{th}}$, while $\rm{(C2)}$ holds for $\epsilon \geq \epsilon_{\rm{th}}$.
	\item $\beta \geq \beta_{\rm{th}}$. Then, $ \epsilon_{\rm{th}} \leq 0$ and $\rm{(C2)}$ holds for all $\epsilon$.
\end{itemize}

Whenever the set of physical parameters falls under $\rm{(C1)}$, the multiplicity is $m_{000} = 1$ and the first elbow coordinates can be read off the $X^0Y^0Z^0$ term in generating functions $G_n(\noisys), G_n(\gamma)$.
If it falls under $\rm{(C2)}$, then $E_{\rm{max}} = E_1$ ($E_{\rm{max}} = E_2$), the multiplicity is $m_{0n0} = 3^n$ ($m_{00n} = 3^n$) and the first elbow coordinates can be read off the $X^0Y^nZ^0$ ($X^0Y^0Z^n$) term in generating functions $G_n(\noisys), G_n(\gamma)$,
\begin{equation}
	(x_0, L_0) =
	\begin{cases}
		\left( \left(\dfrac{e^{-\beta E_0}}{3\Z_\beta}\right)^n, \wn^n \right), &\rm{(C1)}	\vspace{10pt}\\
		\left( \left(\dfrac{e^{-\beta E_{\rm{max}}}}{\Z_\beta}\right)^n, (3u)^n \right). &\rm{(C2)} 
	\end{cases}
\end{equation}

Considering the distillation process in~\cref{eq:msd_thermal}, the Lorenz curves of the initial and target states may each be described by either $\rm{(C1)}$ or $\rm{(C2)}$.
In any case, a necessary distillation constraint can be defined at the location $x_\star = x_0$ of the initial state's first elbow and be expressed as
\begin{equation}\label{eq:first_elbow_constraint}
	\lc{\noisys(\epsilon)\too{n}}{\gamma_\beta}(x_\star) \geq \lc{\noisys(\epsilon')\too{\tt}}{\gamma_\beta}(x_\star).
\end{equation}

Let's focus on the case where both Lorenz curves are described by $\rm{(C1)}$.
This case includes the unital fragment.

The first elbow of the target state is located at $x'_0 = (3Z)^{-\tt} > x_\star$, so in order to find the target state Lorenz curve coordinate $L'_\star$ at location $x_\star$, we can interpolate between the origin and the target state's first elbow, 
\begin{equation}\label{eq:constraint_deriv_temp}
	L'_\star = \frac{x_\star}{x'_0}L'_0 = \left(\frac{e^{-\beta E_0}}{3\Z_\beta}\right)^{n-\tt} \left( \frac{1}{3} - \frac{4}{9} \epsilon' \right)^{\tt}.
\end{equation}
The constraint in~\cref{eq:first_elbow_constraint} therefore holds only if
\begin{align}
	\frac{n}{n'} &\geq \frac{\ln{\Big[ \big( 1-\frac{4}{3}\epsilon' \big)\Z_\beta  e^{\beta E_0} \Big]}}{\ln{\Big[ \big( 1-\frac{4}{3}\epsilon \big)\Z_\beta e^{\beta E_0} \Big]}} \\
	&= \frac{\ln{\big( 1-\frac{4}{3}\epsilon' \big)} - \beta (F_\beta - E_0)}{\ln{\big( 1-\frac{4}{3}\epsilon \big)} - \beta (F_\beta - E_0)},
\end{align}
with $\tt \leq n$ and $\epsilon' \leq \epsilon \leq \epsilon_{\rm{th}}$. 
The free energy of thermal state $\gamma_\beta$ is denoted by
\begin{equation}
	F_\beta \coloneqq \tr[\gamma_\beta H] + \beta^{-1} \tr[\gamma_\beta \ln{\gamma_\beta}] = -\beta^{-1} \ln{\Z_\beta}.
\end{equation}

Moreover, we can obtain an upper bound on thermal fragment distillation rate $R=n'/n$ for pure target Strange states ($\epsilon' = 0$) given by
\begin{equation}
	R \leq R(\beta) \coloneqq 1 - \frac{\ln{\left( \frac{1}{1 - \frac{4}{3}\epsilon} \right)}}{\beta (E_0 - F_\beta)},
\end{equation}
which holds for all finite $n$ with $\tt \leq n$ and $\epsilon' \leq \epsilon \leq \epsilon_{\rm{th}}$. \nick{In fact, it holds for $0 \leq \epsilon \leq \epsilon_*$, where $\epsilon_\star$ is the noise level (lower than $\epsilon_{\rm{th}}$) at which the state conversion turns from $\rm{(C1)} \rightarrow \rm{(C1)}$ to $\rm{(C1)} \rightarrow \rm{(C2)}$. Need to adjust~\cref{fig:distill_bounds_temp} accordingly}
At the limit of high temperature, $\beta \rightarrow 0$, we get $\beta F_\beta \rightarrow -\ln{3}$, and we retrieve the unital fragment bound,
\begin{equation}
	R(\beta) \xrightarrow{\beta \rightarrow 0} \frac{\ln{(3-4\epsilon)}}{\ln{3}}.
\end{equation}
We compare $R(\beta)$ for different values of $\beta$ with the mana bound $R_{\rm{mana}}$ in~\cref{fig:distill_bounds_temp}.
\begin{figure}[h]
    \centering
    \includegraphics[scale=0.5]{figs/distill_bounds_temp.pdf}
    \caption{\textbf{Distillation rate with low noise in thermal fragments.} Distillation rates obtained by majorization $R(\beta)$ for low noise levels $\epsilon \leq \epsilon_{\rm{th}}$ are plotted for different temperatures $\beta^{-1}$ such that $0 \leq \beta \leq \beta_{\rm{th}}$.
    The mana distillation rate $R_{\rm{mana}}$ is given for comparison.
    The Hamiltonian spectrum is simple harmonic, $(E_0, E_1, E_2) = (0,1,2)$.
    As $\beta$ increases, the range of noise levels for which $R(\beta)$ is valid decreases and the distillation bound becomes stricter.
    }
    \label{fig:distill_bounds_temp}
\end{figure}

Our approach also allows for analysis at the limit of low temperature, $\beta \rightarrow \infty$, which is a limit case of $\rm{(C2)}$ with $\beta \geq \beta_{\rm{th}}$.

We consider 
\begin{equation}
	x_\star = x_0 = (e^{-\beta E_{\rm{max}}} / \Z_\beta)^{n}.
\end{equation}
The first elbow of the target state is located at $x'_0 = (e^{-\beta E_{\rm{max}}} / \Z_\beta)^{\tt} > x_\star$, so in order to find the target state Lorenz curve coordinate $L'_\star$ at location $x_\star$, we can interpolate between the origin and the target state's first elbow, 
\begin{equation}\label{eq:constraint_deriv_lowtemp}
	L'_\star = \frac{x_\star}{x'_0}L'_0 = \left(\frac{e^{-\beta E_2}}{\Z_\beta}\right)^{n-\tt} \left( \frac{1}{2} - \frac{1}{6}\epsilon' \right)^{\tt}.
\end{equation}
Therefore, in the low temperature scenario $\beta \geq \beta_{\rm{th}}$, the constraint in~\cref{eq:first_elbow_constraint} holds only if
\begin{align}
	\frac{n}{n'} &\geq \frac{\ln{\Big[ \big( \frac{1}{2}-\frac{1}{6}\epsilon' \big)\Z_\beta e^{\beta E_{\rm{max}}} \Big]}}{\ln{\Big[ \big( \frac{1}{2}-\frac{1}{6}\epsilon \big)\Z_\beta e^{\beta E_{\rm{max}}} \Big]}} \nonumber\\
	&= \frac{\ln{\big( \frac{1}{2}-\frac{1}{6}\epsilon' \big)} + \beta (E_{\rm{max}} - F_\beta)}{\ln{\big( \frac{1}{2}-\frac{1}{6}\epsilon \big)} + \beta (E_{\rm{max}} - F_\beta)},
\end{align}
with $\tt \leq n$ and $\epsilon' \leq \epsilon$.

We can obtain an upper bound on thermal fragment distillation rate $R=n'/n$ for pure target Strange states ($\epsilon' = 0$) in this regime as well. 
It is given by
\begin{equation}
	R \leq R(\beta) \coloneqq 1 - \frac{\ln{\left(\frac{1}{1-\frac{1}{3}\epsilon} \right)}}{-\ln{2} + \beta (E_{\rm{max}} - F_\beta)},
\end{equation}
which holds for all finite $n$ with $\tt \leq n$ and $\epsilon' \leq \epsilon$.
At the zero temperature limit, $F_\beta$ tends to zero, so $R(\beta) \xrightarrow{\beta \rightarrow \infty} 1$.
We compare $R(\beta)$ for different values of $\beta$ with the mana bound $R_{\rm{mana}}$ in~\cref{fig:distill_bounds_lowtemp}.
\begin{figure}[h]
    \centering
    \includegraphics[scale=0.5]{figs/distill_bounds_lowtemp.pdf}
    \caption{\textbf{Distillation rate for low temperatures in thermal fragments.} Distillation rates obtained by majorization $R(\beta)$ in the temperature regime $\beta \geq \beta_{\rm{th}}$ are plotted for different temperatures $\beta^{-1}$.
    The mana distillation rate $R_{\rm{mana}}$ is given for comparison.
    The Hamiltonian spectrum is simple harmonic, $(E_0, E_1, E_2) = (0,1,2)$.
    \nick{Not-so-good bound for low temperatures, other elbows perform a lot better numerically.}
    }
    \label{fig:distill_bounds_lowtemp}
\end{figure}
